---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geotar0

<!-- badges: start -->
<!-- badges: end -->

The goal of geotar0 is to demonstrate a small example of getting imagery for various places. 

We create a target 'locations' with a function in "_targets.R" that is a dataframe of
'location,longitude,latitude' - 'location' is just a name, or address - by default the example provides a set of city names to {tidygeocoder}, edit this as you like. 



## Installation

You can install the development version of geotar0 like so:

``` r
## dependencies ensures we get hypertidy/ximage, which is only Suggests for plotting
remotes::install_github("mdsumner/geotar0", dependencies = TRUE)
```

## Example

This is a basic example which obtains a small quantity of aerial/satellite imagery from
city names. 


```{r example}
targets::tar_make()  ## resulting .tif files are in _targets/tif_files/
library(geotar0)
plot_ims()  ## this plots the images 
```
